---
server: shiny
filters: [surveydown]
---

```{r}
#| context: setup
#| echo: false
#| warning: false
#| message: false

################
# Installation #
################

# Run this in your R Console to install the latest version of the package:
# remotes::install_github("surveydown-dev/surveydown", force = TRUE)

# Run this to install or update the Quarto extension to the latest version:
# surveydown::sd_update_extension()

#################
# Load packages #
#################

# Load the package
library(surveydown)
library(dplyr)

# Run initial setup function (essential - do not delete)
sd_setup()

##################
# Database setup #
##################

# surveydown stores data on a database that you define at https://supabase.com/
# To connect to a database, update the sd_database() function with details
# from your supabase database. For this demo, we set ignore = TRUE, which will
# ignore the settings and won't attempt to connect to the database. This is
# helpful for local testing if you don't want to record testing data in the
# database table. See the documentation for details:
# https://surveydown.org/store-data

db <- sd_database(
  host   = "",
  dbname = "",
  port   = "",
  user   = "",
  table  = "",
  ignore = TRUE
)
```

::: {#welcome .sd-page}

# Demo survey with predefined random labels

> This is a demo survey showcasing the functionality of <a href="https://surveydown.org" target="_blank">surveydown</a>. It doesn't collect any data.
>
> The GitHub repo of this demo can be accessed <a href="https://github.com/surveydown-dev/demo-randomized-question-labels-predefined" target="_blank">here</a>.

Here is a basic "multiple choice" question where the labels are randomly sampled from 1 to 100.

The random samples are grabbed from a **pre-defined** csv file.

If you refresh the page, the options should change.

```{r}
sd_display_question(id = "q1")
```

```{r}
sd_next(next_page = 'page2')
```

:::

::: {#page2 .sd-page}

This is another page in your survey.
```{r}
sd_next(next_page = 'end')
```

:::

::: {#end .sd-page}

This it the last page in the survey

:::

```{r}
#| context: server

source("server.R")

####################################
# Don't change anything below here #
####################################

# The sd_server function initiates your survey - don't change this

sd_server(
  input   = input,
  output  = output,
  session = session,
  config  = config,
  db      = db
)
```
